Naturalness in U(1) extensions of the MSSM

### 2014-12-16 paper/e6ssm-tuning-paper.tex
sketeched out some of the results discussion. very rough, needs details added, expamnsion and improvement of phrasing.

%    - full scatter plots of MSSM and E6SSM, including different
%      M_Z' values
%    - plots of chargino bound impacts
%    - if room, plots for different U(1)' charges

>>>>

Many recent papers have focussed on light stops as allowing natural
SUSY and there has been a lot of theoretical effort to find SUSY
models with a $125$ GeV Higgs bosons while still having light stops
and experimental efforts to search for light stops.  This is entirely
appropriate, however the fine tning problem from the stops depends
crucially on the RG evolution from the GUT scale, since this is how
the squark masses feed into the soft Higgs masses that appear in the
EWSB conditions.

In Fig. \ref{} we fix blah blah bah [Dylan insert details please] and
show how fine tuning varies as we increase the stop masses. However
thius tuning inly really becomes large for very large stop masses.  On
the other hand if cuttoff is increased then stop masses of severalk
TeV can result in tuning of [insert] as shown in Fig.~\ref{}.

%    - full scatter plots of MSSM and E6SSM, including different
%      M_Z' values

Since the stop mass does not have a large impact on the fine tuning
when the cutoff scale is very low we can use this to see more clearly
the impact of the $Z^\prime$ mass on fine tuning. To do se we cjoose a
cutoff of [insert cutoff] look at the fine tuning for two different
values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
current limits and $4.5$ TeV which could be in reach of the LHC run
II, and compare these to the MSSM.

For this we also fix [what we fix + explain different choices to
  before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} we see that as expected the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  Since with such a low cutoff the stop masses have
little impact on the tuning, the tuning here also does not depend much
on the Higgs mass.  However the tuning from the $Z^\prime$ mass
appears already at tree level and is unavoidable regardless of the
cutoff scale chosen.

Therefore the tuning in these models depends on less assumptions than
the tuning which concerns people in the MSSM and the owest tuned
models are adderessed directly with $Z^\prime$ searches.

In the MSSM the tuning can also be attcked more directly by looking at
chargino mass limikts as this rasies $\mu$ directly.  [Stuff aboiut
  chargino limits stiuts, then show plots in MSSM and E6SSM]
%    - plots of chargino bound impacts

The exact level of tuning from the $Z^\prime$ depends on the charges of
the extra $U(1)$ gauge symmetry it is associated with.  In Fig \ref{}
we look at the fine tuning for other U(1) extensions for the same
$Z^\prime$ masses as we did for the E$_6$SSM.
 % - if room, plots for different U(1)' charge Here we see that the As
can be seen in Fig.~\ref{} the severity of the tunings varies quite a
bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These cagres change the
value of the coefficient $d$ in Eq.~\ref{}.  The values of the
coefficient $d$ in each model is [insert], and this determines which
of the models are most tuned.

[We should add some discussion about the $U(1)_I$ and the physics of
  that model here, since it has the lowest tuning.]

Finally we want to emphasise that while in Fig.~\ref{} the E$_6$SSM
looks more fine tuned than the MSSM this is depends on the cutoff
scale.  Indeed in \cite{} a constrained version of the E$_6$SSM, with
the cuttoff at the GUT scale, is considered and there the cE$_6$SSM
was found to be less tuned than the cMSSM. Since a 125 GeV Higgs can
be achieved in the E$_6$SSM with ligher stops, then if the cutoff is
large, the larger stop masses can make that model more
fine tuned due to large RGE effects.

As is shown in Fig.~\cite{} the tuning in the MSSM becomes larger
than that of the E$_6$SSM when the cuttoff scale is ?
